Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2024-06-27 NovelLBM.tex
final coloring

The Lattice-Boltzmann method (LBM) has become a standard tool in numerical fluid mechanics \cite{Kruger_book}, and we therefore only mention the key choices here. Further details can be found in the appendix~\ref{app:LBM} or in literature.
We use a D3Q19 lattice in full three dimensions together with a single relaxation time collision operator.
Our implementation is based on FluidX3D which has been extensively used and validated in earlier publications \cite{lehmann2021, Lehmann.20229da}.
The core of the algorithm is implemented in OpenCL and thus capable of running on GPUs from different vendors.
Non-periodic boundaries are modeled using the half-way bounce back algorithm. To model fixed inflow/outflow, bounce back boundaries using a Dirichlet boundary condition as described by Krüger \textit{et al.} \cite{Kruger_book} are used.

>>>>

The Lattice-Boltzmann method (LBM) has become a standard tool in numerical fluid mechanics \cite{Kruger_book}, and we therefore only mention the key choices here. Further details can be found in the appendix~\ref{app:LBM} or in literature.
We use a D3Q19 lattice in full three dimensions together with a single relaxation time (SRT) collision operator.
Various tests with a multiple relaxation time (MRT) collision operator did not show significant differences.
Our implementation is based on FluidX3D which has been extensively used and validated in earlier publications \cite{lehmann2021, Lehmann.20229da}.
The core of the algorithm is implemented in OpenCL and thus capable of running on GPUs from different vendors.
Non-periodic boundaries are modeled using the half-way bounce back algorithm. To model fixed inflow/outflow, bounce back boundaries using a Dirichlet boundary condition as described by Krüger \textit{et al.} \cite{Kruger_book} are used.
